---
title: "quiz1.Rmd"
author: "Ron Shillinglaw"
date: "Tuesday, December 02, 2014"
output: html_document
---

```{r}
setwd("~/R/coursera/devdataprod-016/quizzes/quiz1")

```
Question 1
Consider the following code for the cars data set
library(manipulate)
myPlot <- function(s) {
    plot(cars$dist - mean(cars$dist), cars$speed - mean(cars$speed))
    abline(0, s)
}
This function plots distance versus speed, each de-meaned and an associated line of slope s. Which of the following code will make a manipulate plot that creates a slider for the slope?
manipulate(myPlot(s), slider = x(0, 2, step = 0.1))
manipulate(myPlot(s), x.s = slider(0, 2, step = 0.1))
manipulate(myPlot, s = slider(0, 2, step = 0.1))
ans1=manipulate(myPlot(s), s = slider(0, 2, step = 0.1))
```{r}
library(manipulate)
myPlot <- function(s) {
    plot(cars$dist - mean(cars$dist), cars$speed - mean(cars$speed))
    abline(0, s)
}


```

Question 2
Which of the following code uses the rCharts package to create a sortable and searchable data table for the airquality data set? Assume the rCharts package and the airquality data set have already been loaded into R.
ans1=dTable(airquality, sPaginationType = "full_numbers")
d <- data.frame(airquality, stringsAsFactors = FALSE) print(d)
airquality
head(airquality)

Question 3
A basic shiny data product requires:
A server.R file only.
ans1=A ui.R and server.R file or a A server.R file and a directory called www containing the relevant html files.
A shiny.R file.
A ui.R file only.

Question 4
What is incorrect about the followig syntax in ui.R?

library(shiny)
shinyUI(pageWithSidebar(
  headerPanel("Data science FTW!"),
  sidebarPanel(
    h2('Big text') # ,
    h3('Sidebar')
  ),
  mainPanel(
      h3('Main Panel text')
  )
))

The h3 command should be an h2 command.
The "Sidebar" should say "Sidebar text".
ans1=Missing a comma in the sidebar panel
The h2 command has the wrong arguments.

Question 5
Consider the following code in ui.R
shinyUI(pageWithSidebar(
  headerPanel("Example plot"),
  sidebarPanel(
    sliderInput('mu', 'Guess at the mu',value = 70, min = 60, max = 80, step = 0.05,)
  ),
  mainPanel(
    plotOutput('newHist')
  )
))


And the following server.R code.

library(UsingR)
data(galton)

shinyServer(
  function(input, output) {
    output$myHist <- renderPlot({
      hist(galton$child, xlab='child height', col='lightblue',main='Histogram')
      mu <- input$mu
      lines(c(mu, mu), c(0, 200),col="red",lwd=5)
      mse <- mean((galton$child - mu)^2)
      text(63, 150, paste("mu = ", mu))
      text(63, 140, paste("MSE = ", round(mse, 2)))
      })
    
  }
)



Why isn't it doing what we want?
ans1=The server.R output name isn't the same as the plotOutput command used in ui.R.
The phrase "Guess at the mu value" should say "mean" instead of "mu"
It should be mu <- input$mean in server.R
The limits of the slider are set incorrectly and giving an error.

```{r}
library(shiny)
setwd("~/R/coursera/devdataprod-016/quizzes/quiz1/question5")



```


