---
title: "quiz2.Rmd"
author: "Ron Shillinglaw"
date: "Monday, December 08, 2014"
output: html_document
---

```{r}
setwd("~/R/coursera/devdataprod-016/quizzes/quiz2")

```


Question 1
In the slidify YAML text. Changing the framework from io2012 to shower does what?
It changes nothing.
It changes whether the document is self contained or requires being connected to the internet.
It changes the ability to display mathjax javascript rendering.
It changes the html5 framework thus changing the style of the slides.
Question 2
You wrote R code in a slidify document as follows
```{r}
fit <- lm(y ~ x1 + x2 + x3)
summary(fit)
```

Question 1
In the slidify YAML text. Changing the framework from io2012 to shower does what?
It changes nothing.
It changes whether the document is self contained or requires being connected to the internet.
It changes the ability to display mathjax javascript rendering.
ans1=It changes the html5 framework thus changing the style of the slides.

Question 2
You wrote R code in a slidify document as follows
```{r}
fit <- lm(y ~ x1 + x2 + x3)
summary(fit)
```

If you want to hide the results of the summary statement (yet still have it run) what should you do?
ans2=Add a results = 'hide' option in the {r} call of the code chunk
Add a echo = FALSE option in the {r} call of the code chunk
Comment out the command # summary(fit)
Comment the command as below but also use a bang symbol after the comment, as in #! summary(fit)

Question 3
You wrote R code in a slidify document as follows
```{r}
fit <- lm(y ~ x1 + x2 + x3)
summary(fit)
```


If you want to display the results, but not the actual code, what should you do?
Comment the command, but use a bang symbol after the comment, as in #! summary(fit)
ans1=Add a echo = FALSE option in the {r} call of the code chunk
Comment out the command # summary(fit)
Add a echo = TRUE option in the {r} call of the code chunk

Question 4
R studio presentation tool does what?
Creates a power point presentation from a generalized markdown format having an extension Rpres.
Creates a presentation that can only be run from within Rstudio.
ans1=Creates HTML5 slides using a generalized markdown format having an extention Rpres and creates reproducible presentations by embedding and running the R code from within the presentation document.
Creates presentable R code from within presentations. However, it does not actually run the code.

Question 5
In Rstudio presenter, if you do not want the code to be evaluated, what option do you need to add to the {r} options?
results = 'hide'
ans1=eval = FALSE
echo = FALSE
run = FALSE

Question 6
When presenting data analysis to a broad audience, which of the following should be done?
wrong ans1=Present results in the chronological order in which it was performed.
Do not include figure captions.
missing in 2nd attempt: Make the figure axes readable.
Show every analysis and method that was done.
ans2=Summarize the problem first.
